---
title: "Subsetting Data for Variables in 'Perceiving through the Grapevine' Manuscript"
author: "Cory K. Costello & Sanjay Srivastava"
date: "last knitted: `r Sys.time()`"
output: html_document
---
# What is this file?

Here I'll read in the full (cleaned, scored, reshaped) datasets, subset them for the variables used in the manuscript (item-level, not scale scores), and write out these subsetted files. For the time being, we're posting just these subsetted files, but will make the full data available in the future. 

# Read in Data
```{r}
library(rio)
library(tidyverse)

study1 <- import("../../Data/Study_1/wide_data/rep_s1_full_wide_data.csv")
study2 <- import("../../Data/Study_2/wide_data/rep_s2_full_wide_data.csv")
```

# Selecting Vars needed in Analyses

## Study 1
```{r}
study1 %>% 
  select(sess_id, 
        # BFI items. Which includes hp items,
        # which are not bfi items, but have bfi
        # in their labels to make thing easy.
         contains("bfi"),
        # IRI items, which all start with B_q or D_q
         starts_with("B_q"),
         starts_with("D_q"),
         # remove ratings we didn't pre-reg/use
         -starts_with("A_B"),
         -starts_with("B_A"),
         -starts_with("C_D"),
         -starts_with("D_C")) %>% 
  export("Data/rep_s1_4ms.csv")
```

## Study 2
```{r}
study2 %>% 
  select(sess_id, 
         condition,
         contains("bfi"),
         # and the social decision qs
         contains("goodleader"),
         contains("goodfriend"),
         # IRI items, which all start with B_q or D_q
         starts_with("B_q"),
         starts_with("D_q"),
         # remove ratings we didn't pre-reg/use
         # remove ratings we didn't pre-reg/use
         -starts_with("A_B"),
         -starts_with("B_A"),
         -starts_with("C_D"),
         -starts_with("D_C")) %>% 
  export("Data/rep_s2_4ms.csv")
```
