---
title: "Profile Analyses (based on JPSP Round 1 reviews)"
author: "MASKED FOR PEER REVIEW"
date: "last knitted: `r Sys.time()`"
output:
    html_document:
      toc: true
      toc_float: true
      code_folding: show
      df_print: paged
---
# Data & Libraries
Here I'll read in the data and load the libraries I'll use, including the `ReputationModelR` package I created for these analyses.
```{r setup, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, cache = TRUE)
# Make sure necessary packages are installed
if("rio" %in% installed.packages()[,1] == FALSE){install.packages("rio")}
if("magrittr" %in% installed.packages()[,1] == FALSE){install.packages("tidyverse")}
if("ReputationModelR" %in% installed.packages()[,1] == FALSE){devtools::install_github("Coryc3133/ReputationModelR")}
if("lme4" %in% installed.packages()[,1] == FALSE){install.packages("lme4")}
if("lmerTest" %in% installed.packages()[,1] == FALSE){install.packages("lmerTest")}
library(rio)
library(tidyverse)
library(ReputationModelR)
library(lme4)
library(lmerTest)
study1 <- import("Data/rep_s1_4ms.csv")
study2 <- import("Data/rep_s2_4ms.csv") %>% 
  # missing condition are "", but need to be NA
  mutate(condition = ifelse(condition == "", NA, condition))
item_eval <- import("Data/rep_BigSix_evaluativeness.csv")
```

## Reshape Study 1 Data for Profile Analyses

```{r study1_reshape_profiles}
study1_profiles <- 
  study1 %>% 
  select(sess_id, contains("bfi")) %>% 
  gather(var, rating, -sess_id) %>%
  separate(var, c("perceiver", "target", "item"), extra = "merge") %>%
  filter(target == "A" | target == "C") %>% 
  mutate(triad_id = 
           case_when(target == "A" ~ "ACD",
                     target == "C" ~ "CAB"),
         rating_type = 
           case_when(perceiver == target ~ "self",
                     perceiver == "B" ~ "p2",
                     perceiver == "D" ~ "p2",
                     TRUE ~ "p1")) %>%
  select(sess_id, triad_id, item, rating_type, rating) %>% 
  spread(rating_type, rating) %>% 
  group_by(item) %>% 
  mutate(., # center at midpoint
         p1 = p1 - 3,
         p2 = p2 -  3,
         self = self - 3,
         self_norm = mean(self, na.rm = TRUE),
         self_dist = self - self_norm,
         p1_norm = mean(p1, na.rm = TRUE),
         p1_dist = p1 - p1_norm)
```

## Reshape Study 2 Data for Profile Analyses

```{r study2_reshape_profiles}
study2_profiles <- 
  study2 %>% 
  select(sess_id, contains("bfi")) %>% 
  gather(var, rating, -sess_id) %>%
  separate(var, c("perceiver", "target", "item"), extra = "merge") %>%
  filter(target == "A" | target == "C") %>% 
  mutate(triad_id = 
           case_when(target == "A" ~ "ACD",
                     target == "C" ~ "CAB"),
         rating_type = 
           case_when(perceiver == target ~ "self",
                     perceiver == "B" ~ "p2",
                     perceiver == "D" ~ "p2",
                     TRUE ~ "p1")) %>%
  select(sess_id, triad_id, item, rating_type, rating) %>% 
  spread(rating_type, rating) %>% 
  group_by(item) %>% 
  mutate(., # center at midpoint
         p1 = p1 - 3,
         p2 = p2 -  3,
         self = self - 3,
         self_norm = mean(self, na.rm = TRUE),
         self_dist = self - self_norm,
         p1_norm = mean(p1, na.rm = TRUE),
         p1_dist = p1 - p1_norm)
```

## ICCs and profile for Item Evaluativeness
### ICC
```{r icc_eval}
item_eval %>% 
  t() %>% 
  psych::ICC()
```
### Calculating Item Evaluativeness Profile
```{r eval_profile}
item_eval_prof <- item_eval %>% 
  gather(item, rating, -subj) %>% 
  # mid-point center it
  mutate(rating = rating - 3) %>% 
  group_by(item) %>% 
  summarize(eval = mean(rating, na.rm = TRUE)) %>% 
  mutate(item = str_to_lower(item),
         item = str_replace_all(item, "bfie_", "bfi_"))
```

#### Joining to other data

```{r join_eval}
# study 1
study1_profiles <- study1_profiles %>% 
  left_join(item_eval_prof)

# study 2
study2_profiles <- study2_profiles %>% 
  left_join(item_eval_prof)

# integrated
study2_profiles <- study2_profiles %>% 
  left_join(item_eval_prof)
```

##  Calculate Scale Scores
Here I'll score the BFI into domain scores and the IRI into its subscales. I'll also produce coefficeint alphas and basic descriptives. 

I'm going to use the `scoreItems()` function from the `psych` package. This both reverse scores items and calculates scale scores. It also provide some information about the scores.

### Study 1 Data: Score Big Six Domains
* agreeableness     = 2, 7, 12R, 17R, 22R, 27, 32, 37R, 42R, 47R, 52, 57
* conscientiousness = 3R, 8R, 13, 18, 23R, 28R, 33, 38, 43, 48R, 53, 58R
* hp                = HP45r HP46r HP47r HP48r HP49r HP50 HP51 HP52
* neuroticism       = 4R, 9R, 14, 19, 24R, 29R, 34, 39, 44R, 49R, 54, 59
* extraversion      = 1, 6, 11R, 16R, 21, 26R, 31R, 36R, 41, 46, 51R, 56
* openness          = 5R, 10, 15, 20, 25R, 30R, 35, 40, 45R, 50R, 55R, 60

For now, first make the key:
```{r make_big6_keys}
# Make keys
big6_keys <- list(
                 agreeableness = c("bfi_2", "bfi_7", "-bfi_12", "-bfi_17", 
                                   "-bfi_22", "bfi_27", "bfi_32", "-bfi_37", 
                                   "-bfi_42", "-bfi_47", "bfi_52", "bfi_57"),
                 conscientiousness = c("-bfi_3", "-bfi_8", "bfi_13", "bfi_18", 
                                       "-bfi_23", "-bfi_28", "bfi_33", "bfi_38", 
                                       "bfi_43", "-bfi_48", "bfi_53", "-bfi_58"),
                 hp = c("-bfi_hp45", "-bfi_hp46", "-bfi_hp47", "-bfi_hp48", 
                            "-bfi_hp49", "bfi_hp50", "bfi_hp51", "bfi_hp52"),
                 neuroticism = c("-bfi_4", "-bfi_9", "bfi_14", "bfi_19", 
                                 "-bfi_24", "-bfi_29", "bfi_34", "bfi_39",
                                 "-bfi_44", "-bfi_49", "bfi_54", "bfi_59"),
                 extraversion = c("bfi_1", "bfi_6", "-bfi_11", "-bfi_16", 
                                  "bfi_21", "-bfi_26", "-bfi_31", "-bfi_36", 
                                  "bfi_41", "bfi_46", "-bfi_51", "bfi_56"),
                 openness = c("-bfi_5", "bfi_10", "bfi_15", "bfi_20", 
                              "-bfi_25", "-bfi_30", "bfi_35", "bfi_40", 
                              "-bfi_45", "-bfi_50", "-bfi_55", "bfi_60"))
```

Next, I'll score the Big Six. I'll turn the data into long format to make things a little easier, since it's the same scoring used for all of the Big Six ratings.
```{r score_big6}
# Lengthen Data
study1_big6_long <- 
study1 %>% 
  select(sess_id, contains("bfi")) %>% 
  gather(variable, rating, -sess_id) %>% 
  separate(variable, 
           c("perceiver", "target", "item"), 
           extra = "merge") %>% 
  spread(item, rating)

# Score long data and bind the scores to
# the end of the long data, then widen it back out
# and call it study1, replacing the raw data
study1 <- 
  psych::scoreItems(big6_keys, 
                    items = study1_big6_long, 
                    impute = "none") %>% 
  .[["scores"]] %>% 
  cbind(study1_big6_long, .) %>% 
  gather(variable, rating, -(1:3)) %>% 
  unite(variable, perceiver, target, variable) %>% 
  spread(variable, rating) %>% 
  select(sess_id,
         ends_with("agreeableness"),
         ends_with("conscientiousness"),
         ends_with("hp"),
         ends_with("neuroticism"),
         ends_with("extraversion"),
         ends_with("openness")) %>% 
  right_join(study1)
```

Finally, I'll get the coefficient alphas for each subscale. 

```{r alphas_big6}
library(kableExtra)

study1_big6_long %>% 
  mutate(rating_type = case_when(perceiver == target ~ "Self",
                               perceiver == "A" & target == "C" |
                                 perceiver == "C" & target == "A" ~ "P1",
                               perceiver == "B" & target == "C" |
                                 perceiver == "D" & target == "A" ~ "P2")) %>% 
  split(.$rating_type) %>% 
  map_df(~ psych::scoreItems(big6_keys,
                          items = .,
                          impute = "none") %>% pluck("alpha")) %>% 
  mutate(domain = names(big6_keys),
         domain = ifelse(domain == "hp", "honesty-propriety", domain)) %>% 
  gather(report, alpha, -domain) %>%
  mutate(report = fct_relevel(report, 
                              "Self",
                              "P1",
                              "P2")) %>% 
  select(report, domain, alpha) %>% 
  arrange(report) %>% 
  knitr::kable(digits = c(NA, NA, 2),
               caption = "Coefficient Alphas for Big Six Ratings Study 1",
               format = "html", escape = F) %>%
  kable_styling("striped", full_width = F)
  
```
### Study 1 Data: Calculate scale scores: IRI

* Empathic Concern = q2_emp, q4_empr, q9_emp, q14_empr, q18_empr, q20_emp, q22_emp

* Fantasy Scale = q1_fs, q5_fs, q7_fsr, q12_fsr, q16_fs, q23_fs, q26_fs

* Personal Distress = q6_pd, q10_pd, q13_pdr, q17_pd, q19_pdr, q24_pd, q27_pd

* Perspective Taking = q3_ptr, q8_pt, q11_pt, q15_ptr, q21_pt, q25_pt, q28_pt


Using the `scoreItems()` function from the psych package again. Then, Ill save out and cbind the scores to the data, and produce a table for the alphas. 

First make the key:
```{r make_keys_iri}
iri_keys <- list(
  iri_empathic = c("q2_emp", "-q4_emp", "q9_emp", "-q14_emp", "-q18_emp", "q20_emp", "q22_emp"),
  iri_fantasy = c("q1_fs", "q5_fs", "-q7_fs", "-q12_fs", "q16_fs", "q23_fs", "q26_fs"),
  iri_distress = c("q6_pd", "q10_pd", "-q13_pd", "q17_pd", "-q19_pd", "q24_pd", "q27_pd"),
  iri_perspective = c("-q3_pt", "q8_pt", "q11_pt", "-q15_pt", "q21_pt", "q25_pt", "q28_pt")
)
```

Next, I'll score the IRI. I'll turn the data into long format like above with the Big Six.
```{r score_iri}
# Lengthen Data
study1_iri_long <- 
study1 %>% 
  select(sess_id, starts_with("B_q"), starts_with("D_q")) %>% 
  gather(variable, rating, -sess_id) %>% 
  separate(variable, 
           c("perceiver", "item"), 
           extra = "merge") %>% 
  spread(item, rating)

# Score long data and bind the scores to
# the end of the long data, then widen it back out
# and call it study1, replacing the raw data
study1 <- 
  psych::scoreItems(iri_keys, 
                    items = study1_iri_long, 
                    impute = "none") %>% 
  .[["scores"]] %>% 
  cbind(study1_iri_long, .) %>% 
  gather(variable, rating, -(1:2)) %>% 
  unite(variable, perceiver, variable) %>% 
  spread(variable, rating) %>% 
  select(sess_id, contains("iri")) %>% 
  right_join(study1)
```

Finally, I'll get the coefficient alphas for each subscale. 

```{r alphas_iri}
library(kableExtra)

 psych::scoreItems(iri_keys, 
                    items = study1_iri_long, 
                    impute = "none") %>% 
  .[["alpha"]] %>% 
   as_tibble() %>% 
   gather(subscale, alpha) %>% 
   mutate(subscale =
            case_when(subscale == "iri_empathic" ~ "empathic concern",
                      subscale == "iri_fantasy" ~ "fantasy",
                      subscale == "iri_distress" ~ "distress tolerance",
                      subscale == "iri_perspective" ~ "perspective taking")) %>% 
  knitr::kable(digits = c(NA, 2),
               caption = "Coefficient Alphas for Perspective Taking Study 1",
               format = "html", escape = F) %>%
  kable_styling("striped", full_width = F)
  
```

### Study 2 Data: Score Big Six Domains
Same scoring & keys as Study 2. Basically just the dataframes are different, and the rest is the same.
```{r score_big6_s2}
# Lengthen Data
study2_big6_long <- 
study2 %>% 
  select(sess_id, contains("bfi")) %>% 
  gather(variable, rating, -sess_id) %>% 
  separate(variable, 
           c("perceiver", "target", "item"), 
           extra = "merge") %>% 
  spread(item, rating)

# Score long data and bind the scores to
# the end of the long data, then widen it back out
# and call it study2, replacing the raw data
study2 <- 
  psych::scoreItems(big6_keys, 
                    items = study2_big6_long, 
                    impute = "none") %>% 
  .[["scores"]] %>% 
  cbind(study2_big6_long, .) %>% 
  gather(variable, rating, -(1:3)) %>% 
  unite(variable, perceiver, target, variable) %>% 
  spread(variable, rating) %>% 
  select(sess_id,
         ends_with("agreeableness"),
         ends_with("conscientiousness"),
         ends_with("hp"),
         ends_with("neuroticism"),
         ends_with("extraversion"),
         ends_with("openness")) %>% 
  right_join(study2)
```

Finally, I'll get the coefficient alphas for each subscale. 

```{r alphas_big6_s2}
library(kableExtra)

study2_big6_long %>% 
  mutate(rating_type = case_when(perceiver == target ~ "Self",
                               perceiver == "A" & target == "C" |
                                 perceiver == "C" & target == "A" ~ "P1",
                               perceiver == "B" & target == "C" |
                                 perceiver == "D" & target == "A" ~ "P2")) %>% 
  split(.$rating_type) %>% 
  map_df(~ psych::scoreItems(big6_keys,
                          items = .,
                          impute = "none") %>% pluck("alpha")) %>% 
  mutate(domain = names(big6_keys),
         domain = ifelse(domain == "hp", "honesty-propriety", domain)) %>% 
  gather(report, alpha, -domain) %>%
  mutate(report = fct_relevel(report, 
                              "Self",
                              "P1",
                              "P2")) %>% 
  select(report, domain, alpha) %>% 
  arrange(report) %>% 
  knitr::kable(digits = c(NA, NA, 2),
               caption = "Coefficient Alphas for Big Six Ratings Study 2",
               format = "html", escape = F) %>%
  kable_styling("striped", full_width = F)
  
```

### Study 2 Data: Calculate scale scores: IRI
Same keys as before

Next, I'll score the IRI. I'll turn the data into long format like above with the Big Six.
```{r score_iri_s2}
# Lengthen Data
study2_iri_long <- 
study2 %>% 
  select(sess_id, starts_with("B_q"), starts_with("D_q")) %>% 
  gather(variable, rating, -sess_id) %>% 
  separate(variable, 
           c("perceiver", "item"), 
           extra = "merge") %>% 
  spread(item, rating)

# Score long data and bind the scores to
# the end of the long data, then widen it back out
# and call it study2, replacing the raw data
study2 <- 
  psych::scoreItems(iri_keys, 
                    items = study2_iri_long, 
                    impute = "none") %>% 
  .[["scores"]] %>% 
  cbind(study2_iri_long, .) %>% 
  gather(variable, rating, -(1:2)) %>% 
  unite(variable, perceiver, variable) %>% 
  spread(variable, rating) %>% 
  select(sess_id, contains("iri")) %>% 
  right_join(study2)
```

Finally, I'll get the coefficient alphas for each subscale. 

```{r alphas_iri_s2}
library(kableExtra)

 psych::scoreItems(iri_keys, 
                    items = study2_iri_long, 
                    impute = "none") %>% 
  .[["alpha"]] %>% 
   as_tibble() %>% 
   gather(subscale, alpha) %>% 
   mutate(subscale =
            case_when(subscale == "iri_empathic" ~ "empathic concern",
                      subscale == "iri_fantasy" ~ "fantasy",
                      subscale == "iri_distress" ~ "distress tolerance",
                      subscale == "iri_perspective" ~ "perspective taking")) %>% 
  knitr::kable(digits = c(NA, 2),
               caption = "Coefficient Alphas for Perspective Taking Study 2",
               format = "html", escape = F) %>%
  kable_styling("striped", full_width = F)
  
```


# Study 1 Hearsay SAM
## Self-P1 & Self-P2 in same model

### Level 1 Equation:
$P_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distance_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distance_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distance_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distance_{tg} + r_{2tg}$    

### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_sam}
study1_profiles2 <- study1_profiles %>% 
  select(sess_id, triad_id, item, self_norm, self_dist, eval, p1, p2) %>% 
  gather(distance, rating, -(sess_id:eval))

study1_accuracy_sam_combined <- lmer(rating ~ self_norm + self_dist + eval + distance +
                               distance:self_norm + distance:self_dist + distance:eval +
                               (1 + self_norm + self_dist + distance +
                                  distance:self_norm + distance:self_dist + distance:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles2)
summary(study1_accuracy_sam_combined)
```

### Simple Slope for p2

```{r study1_simple_accuracy_p2}

study1_accuracy_simple_sam_p2 <- lmer(rating ~ self_norm + self_dist + eval +
                               (1 + self_norm + self_dist + eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_combined)
```

## P1-P2 Agreement 

### Level 1 Equation:
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + r_{3tg}$

### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$  
$\beta_{30g} = \gamma_{300} + u_{30g}$  

*i* = item; *t* = triad; *g* = group
```{r study1_p1p2_consensus_sam}
study1_consensus_sam <- lmer(p2 ~ p1_norm + p1_dist + eval +
                         (1 + p1_norm + p1_dist + eval | sess_id/triad_id),
                       data = study1_profiles)

summary(study1_consensus_sam)
```

## Extraversion Moderators

### adding target, P1, and P2 Extraversion to profile data

```{r study1_add_extr_to_profs}
# joining in target Extraversion
study1_profiles <- study1 %>% 
  select(sess_id, ends_with("extraversion")) %>% 
  gather(var, t_ext, -sess_id) %>% 
  separate(var, c("perceiver", "target", "variable")) %>%
  filter(perceiver == target & perceiver == "A" | 
         perceiver == target & perceiver == "C") %>%
  mutate(triad_id = ifelse(target == "A", "ACD", "CAB")) %>%
  mutate(t_ext_cent = t_ext - mean(t_ext, na.rm = TRUE)) %>% 
  select(sess_id, triad_id, t_ext_cent) %>% 
  right_join(study1_profiles)

# joining in P1 Extraversion
study1_profiles <- study1 %>% 
  select(sess_id, ends_with("extraversion")) %>% 
  gather(var, p1_ext, -sess_id) %>% 
  separate(var, c("perceiver", "target", "variable")) %>%
  filter(perceiver == "A" & target == "C" | 
         perceiver == "C" & target == "A") %>%
  mutate(triad_id = ifelse(target == "A", "ACD", "CAB")) %>%
  mutate(p1_ext_cent = p1_ext - mean(p1_ext, na.rm = TRUE)) %>% 
  select(sess_id, triad_id, p1_ext_cent) %>% 
  right_join(study1_profiles)

# joining in P2 Extraversion

study1_profiles <- study1 %>% 
  select(sess_id, ends_with("extraversion")) %>% 
  gather(var, p2_ext, -sess_id) %>% 
  separate(var, c("perceiver", "target", "variable")) %>%
  filter(perceiver == "B" & target == "C" | 
         perceiver == "D" & target == "A") %>%
  mutate(triad_id = ifelse(target == "A", "ACD", "CAB")) %>%
  mutate(p2_ext_cent = p2_ext - mean(p2_ext, na.rm = TRUE)) %>% 
  select(sess_id, triad_id, p2_ext_cent) %>% 
  right_join(study1_profiles)
```

### Extraversion Moderating Hearsay Consensus
#### Target Extraversion moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}targetExtraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}targetExtraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}targetExtraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}targetExtraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_target_ext_sam}
study1_consensus_sam_t_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + t_ext_cent +
                               t_ext_cent:p1_norm + t_ext_cent:p1_dist + t_ext_cent:eval +
                               (1 + p1_norm + p1_dist + t_ext_cent +
                                  t_ext_cent:p1_norm + t_ext_cent:p1_dist + t_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_t_ext)
```

#### P1 Extraversion moderating Hearsay Consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P1Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P1Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P1Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P1Extraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_p1_ext_sam}
study1_consensus_sam_p1_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + p1_ext_cent +
                               p1_ext_cent:p1_norm + p1_ext_cent:p1_dist + p1_ext_cent:eval +
                               (1 + p1_norm + p1_dist + p1_ext_cent +
                                  p1_ext_cent:p1_norm + p1_ext_cent:p1_dist + p1_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_p1_ext)
```

#### P2 Extraversion moderating Hearsay Consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P2Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P2Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P2Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P2Extraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_p2_ext_sam}
study1_consensus_sam_p2_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + p2_ext_cent +
                               p2_ext_cent:p1_norm + p2_ext_cent:p1_dist + p2_ext_cent:eval +
                               (1 + p1_norm + p1_dist + p2_ext_cent +
                                  p2_ext_cent:p1_norm + p2_ext_cent:p1_dist + p2_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_p2_ext)
```

### Extraversion Moderating Hearsay Accuracy
#### Target Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}targetExtraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}targetExtraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}targetExtraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}targetExtraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_target_ext_sam}
study1_accuracy_sam_t_ext <- lmer(p2 ~ self_norm + self_dist + eval + t_ext_cent +
                               t_ext_cent:self_norm + t_ext_cent:self_dist + t_ext_cent:eval +
                               (1 + self_norm + self_dist + t_ext_cent +
                                  t_ext_cent:self_norm + t_ext_cent:self_dist + t_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_t_ext)
```

#### P1 Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P1Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P1Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P1Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P1Extraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_p1_ext_sam}
study1_accuracy_sam_p1_ext <- lmer(p2 ~ self_norm + self_dist + eval + p1_ext_cent +
                               p1_ext_cent:self_norm + p1_ext_cent:self_dist + p1_ext_cent:eval +
                               (1 + self_norm + self_dist + p1_ext_cent +
                                  p1_ext_cent:self_norm + p1_ext_cent:self_dist + p1_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_p1_ext)
```

#### P2 Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P2Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P2Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P2Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P2Extraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_p2_ext_sam}
study1_accuracy_sam_p2_ext <- lmer(p2 ~ self_norm + self_dist + eval + p2_ext_cent +
                               p2_ext_cent:self_norm + p2_ext_cent:self_dist + p2_ext_cent:eval +
                               (1 + self_norm + self_dist + p2_ext_cent +
                                  p2_ext_cent:self_norm + 
                                  p2_ext_cent:self_dist + p2_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(accuracy_sam_p2_ext)
```

## Empathy Moderators

### adding P2 Empathy to profile data

```{r study1_adding_emp_profs}
# joining in P2 Empathy
study1_profiles <- study1 %>% 
  select(sess_id, B_iri_distress, B_iri_empathic, B_iri_fantasy, B_iri_perspective,
         D_iri_distress, D_iri_empathic, D_iri_fantasy, D_iri_perspective) %>% 
  gather(var, value, -sess_id) %>% 
  separate(var, c("p2", "elim", "variable")) %>%
  mutate(triad_id = ifelse(p2 == "B", "CAB", "ACD")) %>%
  spread(variable, value) %>% 
  mutate(distress_cent = distress - mean(distress, na.rm = TRUE),
         empathic_cent = empathic - mean(empathic, na.rm = TRUE),
         fantasy_cent = fantasy - mean(fantasy, na.rm = TRUE),
         perspective_cent = perspective - mean(perspective, na.rm = TRUE))%>% 
  select(sess_id, triad_id, distress_cent, empathic_cent,
         fantasy_cent, perspective_cent) %>% 
  right_join(study1_profiles)
```

### Empathy Moderating Consensus
#### Distress moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distress_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distress_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distress_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distress_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_distress}
study1_consensus_sam_distress <- lmer(p2 ~ p1_norm + p1_dist + eval + distress_cent +
                               distress_cent:p1_norm + distress_cent:p1_dist + 
                                 distress_cent:eval +
                               (1 + p1_norm + p1_dist + distress_cent +
                                  distress_cent:p1_norm + 
                                  distress_cent:p1_dist + distress_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_distress)
```

#### Empathic Concern moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}EmpathicConcern_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}EmpathicConcern_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}EmpathicConcern_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}EmpathicConcern_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_empathic}
study1_consensus_sam_empathic <- lmer(p2 ~ p1_norm + p1_dist + eval + empathic_cent +
                               empathic_cent:p1_norm + 
                                 empathic_cent:p1_dist + empathic_cent:eval +
                               (1 + p1_norm + p1_dist + empathic_cent +
                                  empathic_cent:p1_norm + 
                                  empathic_cent:p1_dist + empathic_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_empathic)
```

#### Fantasy moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Fantasy_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Fantasy_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Fantasy_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Fantasy_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_fantasy}
study1_consensus_sam_fantasy <- lmer(p2 ~ p1_norm + p1_dist + eval + fantasy_cent +
                               fantasy_cent:p1_norm + fantasy_cent:p1_dist + 
                                 fantasy_cent:eval +
                               (1 + p1_norm + p1_dist + fantasy_cent +
                                  fantasy_cent:p1_norm + fantasy_cent:p1_dist + 
                                  fantasy_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_fantasy)
```

### Perspective Taking moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}PerspectiveTaking_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}PerspectiveTaking_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}PerspectiveTaking_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}PerspectiveTaking_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_consensus_x_perspective}
study1_consensus_sam_perspective <- lmer(p2 ~ p1_norm + p1_dist + eval + perspective_cent +
                               perspective_cent:p1_norm + 
                                 perspective_cent:p1_dist + perspective_cent:eval +
                               (1 + p1_norm + p1_dist + perspective_cent +
                                  perspective_cent:p1_norm + 
                                  perspective_cent:p1_dist + perspective_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_consensus_sam_perspective)
```

### Empathy Moderating Accuracy
#### Distress moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distress_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distress_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distress_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distress_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_distress}
study1_accuracy_sam_distress <- lmer(p2 ~ self_norm + self_dist + eval + distress_cent +
                               distress_cent:self_norm + distress_cent:self_dist +
                                 distress_cent:eval +
                               (1 + self_norm + self_dist + distress_cent +
                                  distress_cent:self_norm + 
                                  distress_cent:self_dist + distress_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_distress)
```

#### Empathic Concern moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}EmpathicConcern_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}EmpathicConcern_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}EmpathicConcern_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}EmpathicConcern_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_empathic}
study1_accuracy_sam_empathic <- lmer(p2 ~ self_norm + self_dist + eval + empathic_cent +
                               empathic_cent:self_norm + empathic_cent:self_dist + 
                                 empathic_cent:eval +
                               (1 + self_norm + self_dist + empathic_cent +
                                  empathic_cent:self_norm + 
                                  empathic_cent:self_dist + empathic_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_empathic)
```

#### Fantasy moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Fantasy_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Fantasy_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Fantasy_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Fantasy_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_fantasy}
study1_accuracy_sam_fantasy <- lmer(p2 ~ self_norm + self_dist + eval + fantasy_cent +
                               fantasy_cent:self_norm +
                                 fantasy_cent:self_dist + fantasy_cent:eval +
                               (1 + self_norm + self_dist + fantasy_cent +
                                  fantasy_cent:self_norm + 
                                  fantasy_cent:self_dist + fantasy_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_fantasy)
```

#### Perspective Taking moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}PerspectiveTaking_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}PerspectiveTaking_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}PerspectiveTaking_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}PerspectiveTaking_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study1_accuracy_x_perspective}
study1_accuracy_sam_perspective <- lmer(p2 ~ self_norm + self_dist + eval + perspective_cent +
                               perspective_cent:self_norm + 
                                 perspective_cent:self_dist + perspective_cent:eval +
                               (1 + self_norm + self_dist + perspective_cent +
                                  perspective_cent:self_norm + 
                                  perspective_cent:self_dist + perspective_cent:eval | 
                                  sess_id/triad_id),
                             data = study1_profiles)
summary(study1_accuracy_sam_perspective)
```
# Study 2 Hearsay SAM
## Self-P1 & Self-P2 in same model

### Level 1 Equation:
$P_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distance_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distance_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distance_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distance_{tg} + r_{2tg}$    

### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_sam}
study2_profiles2 <- study2_profiles %>% 
  select(sess_id, triad_id, item, self_norm, self_dist, eval, p1, p2) %>% 
  gather(distance, rating, -(sess_id:eval))

study2_accuracy_sam_combined <- lmer(rating ~ self_norm + self_dist + eval + distance +
                               distance:self_norm + distance:self_dist + distance:eval +
                               (1 + self_norm + self_dist + distance +
                                  distance:self_norm + distance:self_dist + distance:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles2)
summary(study2_accuracy_sam_combined)
```

### Simple Slope for p2

```{r study2_simple_accuracy_p2}

study2_accuracy_simple_sam_p2 <- lmer(rating ~ self_norm + self_dist + eval +
                               (1 + self_norm + self_dist + eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_combined)
```

## P1-P2 Agreement 

### Level 1 Equation:
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + r_{3tg}$

### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$  
$\beta_{30g} = \gamma_{300} + u_{30g}$  

*i* = item; *t* = triad; *g* = group
```{r study2_p1p2_consensus_sam}
study2_consensus_sam <- lmer(p2 ~ p1_norm + p1_dist + eval +
                         (1 + p1_norm + p1_dist + eval | sess_id/triad_id),
                       data = study2_profiles)

summary(study2_consensus_sam)
```

## Extraversion Moderators

### adding target, P1, and P2 Extraversion to profile data

```{r study2_add_extr_to_profs}
# joining in target Extraversion
study2_profiles <- study2 %>% 
  select(sess_id, ends_with("extraversion")) %>% 
  gather(var, t_ext, -sess_id) %>% 
  separate(var, c("perceiver", "target", "variable")) %>%
  filter(perceiver == target & perceiver == "A" | 
         perceiver == target & perceiver == "C") %>%
  mutate(triad_id = ifelse(target == "A", "ACD", "CAB")) %>%
  mutate(t_ext_cent = t_ext - mean(t_ext, na.rm = TRUE)) %>% 
  select(sess_id, triad_id, t_ext_cent) %>% 
  right_join(study2_profiles)

# joining in P1 Extraversion
study2_profiles <- study2 %>% 
  select(sess_id, ends_with("extraversion")) %>% 
  gather(var, p1_ext, -sess_id) %>% 
  separate(var, c("perceiver", "target", "variable")) %>%
  filter(perceiver == "A" & target == "C" | 
         perceiver == "C" & target == "A") %>%
  mutate(triad_id = ifelse(target == "A", "ACD", "CAB")) %>%
  mutate(p1_ext_cent = p1_ext - mean(p1_ext, na.rm = TRUE)) %>% 
  select(sess_id, triad_id, p1_ext_cent) %>% 
  right_join(study2_profiles)

# joining in P2 Extraversion

study2_profiles <- study2 %>% 
  select(sess_id, ends_with("extraversion")) %>% 
  gather(var, p2_ext, -sess_id) %>% 
  separate(var, c("perceiver", "target", "variable")) %>%
  filter(perceiver == "B" & target == "C" | 
         perceiver == "D" & target == "A") %>%
  mutate(triad_id = ifelse(target == "A", "ACD", "CAB")) %>%
  mutate(p2_ext_cent = p2_ext - mean(p2_ext, na.rm = TRUE)) %>% 
  select(sess_id, triad_id, p2_ext_cent) %>% 
  right_join(study2_profiles)
```

### Extraversion Moderating Hearsay Consensus
#### Target Extraversion moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}targetExtraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}targetExtraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}targetExtraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}targetExtraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_target_ext_sam}
study2_consensus_sam_t_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + t_ext_cent +
                               t_ext_cent:p1_norm + t_ext_cent:p1_dist + t_ext_cent:eval +
                               (1 + p1_norm + p1_dist + t_ext_cent +
                                  t_ext_cent:p1_norm + t_ext_cent:p1_dist + t_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_t_ext)
```

#### P1 Extraversion moderating Hearsay Consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P1Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P1Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P1Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P1Extraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_p1_ext_sam}
study2_consensus_sam_p1_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + p1_ext_cent +
                               p1_ext_cent:p1_norm + p1_ext_cent:p1_dist + p1_ext_cent:eval +
                               (1 + p1_norm + p1_dist + p1_ext_cent +
                                  p1_ext_cent:p1_norm + p1_ext_cent:p1_dist + p1_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_p1_ext)
```

#### P2 Extraversion moderating Hearsay Consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P2Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P2Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P2Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P2Extraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_p2_ext_sam}
study2_consensus_sam_p2_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + p2_ext_cent +
                               p2_ext_cent:p1_norm + p2_ext_cent:p1_dist + p2_ext_cent:eval +
                               (1 + p1_norm + p1_dist + p2_ext_cent +
                                  p2_ext_cent:p1_norm + p2_ext_cent:p1_dist + p2_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_p2_ext)
```

### Extraversion Moderating Hearsay Accuracy
#### Target Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}targetExtraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}targetExtraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}targetExtraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}targetExtraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_target_ext_sam}
study2_accuracy_sam_t_ext <- lmer(p2 ~ self_norm + self_dist + eval + t_ext_cent +
                               t_ext_cent:self_norm + t_ext_cent:self_dist + t_ext_cent:eval +
                               (1 + self_norm + self_dist + t_ext_cent +
                                  t_ext_cent:self_norm + t_ext_cent:self_dist + t_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_t_ext)
```

#### P1 Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P1Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P1Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P1Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P1Extraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_p1_ext_sam}
study2_accuracy_sam_p1_ext <- lmer(p2 ~ self_norm + self_dist + eval + p1_ext_cent +
                               p1_ext_cent:self_norm + p1_ext_cent:self_dist + p1_ext_cent:eval +
                               (1 + self_norm + self_dist + p1_ext_cent +
                                  p1_ext_cent:self_norm + p1_ext_cent:self_dist + p1_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_p1_ext)
```

#### P2 Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P2Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P2Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P2Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P2Extraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_p2_ext_sam}
study2_accuracy_sam_p2_ext <- lmer(p2 ~ self_norm + self_dist + eval + p2_ext_cent +
                               p2_ext_cent:self_norm + p2_ext_cent:self_dist + p2_ext_cent:eval +
                               (1 + self_norm + self_dist + p2_ext_cent +
                                  p2_ext_cent:self_norm + 
                                  p2_ext_cent:self_dist + p2_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(accuracy_sam_p2_ext)
```

## Empathy Moderators

### adding P2 Empathy to profile data

```{r study2_adding_emp_profs}
# joining in P2 Empathy
study2_profiles <- study2 %>% 
  select(sess_id, B_iri_distress, B_iri_empathic, B_iri_fantasy, B_iri_perspective,
         D_iri_distress, D_iri_empathic, D_iri_fantasy, D_iri_perspective) %>% 
  gather(var, value, -sess_id) %>% 
  separate(var, c("p2", "elim", "variable")) %>%
  mutate(triad_id = ifelse(p2 == "B", "CAB", "ACD")) %>%
  spread(variable, value) %>% 
  mutate(distress_cent = distress - mean(distress, na.rm = TRUE),
         empathic_cent = empathic - mean(empathic, na.rm = TRUE),
         fantasy_cent = fantasy - mean(fantasy, na.rm = TRUE),
         perspective_cent = perspective - mean(perspective, na.rm = TRUE))%>% 
  select(sess_id, triad_id, distress_cent, empathic_cent,
         fantasy_cent, perspective_cent) %>% 
  right_join(study2_profiles)
```

### Empathy Moderating Consensus
#### Distress moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distress_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distress_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distress_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distress_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_distress}
study2_consensus_sam_distress <- lmer(p2 ~ p1_norm + p1_dist + eval + distress_cent +
                               distress_cent:p1_norm + distress_cent:p1_dist + 
                                 distress_cent:eval +
                               (1 + p1_norm + p1_dist + distress_cent +
                                  distress_cent:p1_norm + 
                                  distress_cent:p1_dist + distress_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_distress)
```

#### Empathic Concern moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}EmpathicConcern_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}EmpathicConcern_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}EmpathicConcern_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}EmpathicConcern_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_empathic}
study2_consensus_sam_empathic <- lmer(p2 ~ p1_norm + p1_dist + eval + empathic_cent +
                               empathic_cent:p1_norm + 
                                 empathic_cent:p1_dist + empathic_cent:eval +
                               (1 + p1_norm + p1_dist + empathic_cent +
                                  empathic_cent:p1_norm + 
                                  empathic_cent:p1_dist + empathic_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_empathic)
```

#### Fantasy moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Fantasy_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Fantasy_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Fantasy_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Fantasy_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_fantasy}
study2_consensus_sam_fantasy <- lmer(p2 ~ p1_norm + p1_dist + eval + fantasy_cent +
                               fantasy_cent:p1_norm + fantasy_cent:p1_dist + 
                                 fantasy_cent:eval +
                               (1 + p1_norm + p1_dist + fantasy_cent +
                                  fantasy_cent:p1_norm + fantasy_cent:p1_dist + 
                                  fantasy_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_fantasy)
```

### Perspective Taking moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}PerspectiveTaking_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}PerspectiveTaking_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}PerspectiveTaking_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}PerspectiveTaking_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_consensus_x_perspective}
study2_consensus_sam_perspective <- lmer(p2 ~ p1_norm + p1_dist + eval + perspective_cent +
                               perspective_cent:p1_norm + 
                                 perspective_cent:p1_dist + perspective_cent:eval +
                               (1 + p1_norm + p1_dist + perspective_cent +
                                  perspective_cent:p1_norm + 
                                  perspective_cent:p1_dist + perspective_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_consensus_sam_perspective)
```

### Empathy Moderating Accuracy
#### Distress moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distress_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distress_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distress_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distress_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_distress}
study2_accuracy_sam_distress <- lmer(p2 ~ self_norm + self_dist + eval + distress_cent +
                               distress_cent:self_norm + distress_cent:self_dist +
                                 distress_cent:eval +
                               (1 + self_norm + self_dist + distress_cent +
                                  distress_cent:self_norm + 
                                  distress_cent:self_dist + distress_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_distress)
```

#### Empathic Concern moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}EmpathicConcern_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}EmpathicConcern_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}EmpathicConcern_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}EmpathicConcern_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_empathic}
study2_accuracy_sam_empathic <- lmer(p2 ~ self_norm + self_dist + eval + empathic_cent +
                               empathic_cent:self_norm + empathic_cent:self_dist + 
                                 empathic_cent:eval +
                               (1 + self_norm + self_dist + empathic_cent +
                                  empathic_cent:self_norm + 
                                  empathic_cent:self_dist + empathic_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_empathic)
```

#### Fantasy moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Fantasy_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Fantasy_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Fantasy_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Fantasy_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_fantasy}
study2_accuracy_sam_fantasy <- lmer(p2 ~ self_norm + self_dist + eval + fantasy_cent +
                               fantasy_cent:self_norm +
                                 fantasy_cent:self_dist + fantasy_cent:eval +
                               (1 + self_norm + self_dist + fantasy_cent +
                                  fantasy_cent:self_norm + 
                                  fantasy_cent:self_dist + fantasy_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_fantasy)
```

#### Perspective Taking moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}PerspectiveTaking_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}PerspectiveTaking_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}PerspectiveTaking_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}PerspectiveTaking_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r study2_accuracy_x_perspective}
study2_accuracy_sam_perspective <- lmer(p2 ~ self_norm + self_dist + eval + perspective_cent +
                               perspective_cent:self_norm + 
                                 perspective_cent:self_dist + perspective_cent:eval +
                               (1 + self_norm + self_dist + perspective_cent +
                                  perspective_cent:self_norm + 
                                  perspective_cent:self_dist + perspective_cent:eval | 
                                  sess_id/triad_id),
                             data = study2_profiles)
summary(study2_accuracy_sam_perspective)
```
# Integrated Hearsay SAM

## Combining Study 1 and 2 for integrated analyses

```{r combine_data}
integrated_profiles <- 
  rbind(study1_profiles, study2_profiles)
```

## Self-P1 & Self-P2 in same model

### Level 1 Equation:
$P_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distance_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distance_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distance_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distance_{tg} + r_{2tg}$    

### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_sam}
integrated_profiles2 <- integrated_profiles %>% 
  select(sess_id, triad_id, item, self_norm, self_dist, eval, p1, p2) %>% 
  gather(distance, rating, -(sess_id:eval))

integrated_accuracy_sam_combined <- lmer(rating ~ self_norm + self_dist + eval + distance +
                               distance:self_norm + distance:self_dist + distance:eval +
                               (1 + self_norm + self_dist + distance +
                                  distance:self_norm + distance:self_dist + distance:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles2)
summary(integrated_accuracy_sam_combined)
```

### Simple Slope for p2

```{r integrated_simple_accuracy_p2}

integrated_accuracy_simple_sam_p2 <- lmer(rating ~ self_norm + self_dist + eval +
                               (1 + self_norm + self_dist + eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_combined)
```

## P1-P2 Agreement 

### Level 1 Equation:
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + r_{3tg}$

### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$  
$\beta_{30g} = \gamma_{300} + u_{30g}$  

*i* = item; *t* = triad; *g* = group
```{r integrated_p1p2_consensus_sam}
integrated_consensus_sam <- lmer(p2 ~ p1_norm + p1_dist + eval +
                         (1 + p1_norm + p1_dist + eval | sess_id/triad_id),
                       data = integrated_profiles)

summary(integrated_consensus_sam)
```

## Extraversion Moderators

### Extraversion Moderating Hearsay Consensus
#### Target Extraversion moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}targetExtraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}targetExtraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}targetExtraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}targetExtraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_target_ext_sam}
integrated_consensus_sam_t_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + t_ext_cent +
                               t_ext_cent:p1_norm + t_ext_cent:p1_dist + t_ext_cent:eval +
                               (1 + p1_norm + p1_dist + t_ext_cent +
                                  t_ext_cent:p1_norm + t_ext_cent:p1_dist + t_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_t_ext)
```

#### P1 Extraversion moderating Hearsay Consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P1Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P1Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P1Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P1Extraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_p1_ext_sam}
integrated_consensus_sam_p1_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + p1_ext_cent +
                               p1_ext_cent:p1_norm + p1_ext_cent:p1_dist + p1_ext_cent:eval +
                               (1 + p1_norm + p1_dist + p1_ext_cent +
                                  p1_ext_cent:p1_norm + p1_ext_cent:p1_dist + p1_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_p1_ext)
```

#### P2 Extraversion moderating Hearsay Consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P2Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P2Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P2Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P2Extraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_p2_ext_sam}
integrated_consensus_sam_p2_ext <- lmer(p2 ~ p1_norm + p1_dist + eval + p2_ext_cent +
                               p2_ext_cent:p1_norm + p2_ext_cent:p1_dist + p2_ext_cent:eval +
                               (1 + p1_norm + p1_dist + p2_ext_cent +
                                  p2_ext_cent:p1_norm + p2_ext_cent:p1_dist + p2_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_p2_ext)
```

### Extraversion Moderating Hearsay Accuracy
#### Target Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}targetExtraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}targetExtraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}targetExtraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}targetExtraversion_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_target_ext_sam}
integrated_accuracy_sam_t_ext <- lmer(p2 ~ self_norm + self_dist + eval + t_ext_cent +
                               t_ext_cent:self_norm + t_ext_cent:self_dist + t_ext_cent:eval +
                               (1 + self_norm + self_dist + t_ext_cent +
                                  t_ext_cent:self_norm + t_ext_cent:self_dist + t_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_t_ext)
```

#### P1 Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P1Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P1Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P1Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P1Extraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_p1_ext_sam}
integrated_accuracy_sam_p1_ext <- lmer(p2 ~ self_norm + self_dist + eval + p1_ext_cent +
                               p1_ext_cent:self_norm + p1_ext_cent:self_dist + p1_ext_cent:eval +
                               (1 + self_norm + self_dist + p1_ext_cent +
                                  p1_ext_cent:self_norm + p1_ext_cent:self_dist + p1_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_p1_ext)
```

#### P2 Extraversion moderating Hearsay Accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}P2Extraversion_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}P2Extraversion_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}P2Extraversion_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}P2Extraversion_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_p2_ext_sam}
integrated_accuracy_sam_p2_ext <- lmer(p2 ~ self_norm + self_dist + eval + p2_ext_cent +
                               p2_ext_cent:self_norm + p2_ext_cent:self_dist + p2_ext_cent:eval +
                               (1 + self_norm + self_dist + p2_ext_cent +
                                  p2_ext_cent:self_norm + 
                                  p2_ext_cent:self_dist + p2_ext_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(accuracy_sam_p2_ext)
```

## Empathy Moderators

### adding P2 Empathy to profile data

```{r integrated_adding_emp_profs}
# joining in P2 Empathy
integrated_profiles <- integrated %>% 
  select(sess_id, B_iri_distress, B_iri_empathic, B_iri_fantasy, B_iri_perspective,
         D_iri_distress, D_iri_empathic, D_iri_fantasy, D_iri_perspective) %>% 
  gather(var, value, -sess_id) %>% 
  separate(var, c("p2", "elim", "variable")) %>%
  mutate(triad_id = ifelse(p2 == "B", "CAB", "ACD")) %>%
  spread(variable, value) %>% 
  mutate(distress_cent = distress - mean(distress, na.rm = TRUE),
         empathic_cent = empathic - mean(empathic, na.rm = TRUE),
         fantasy_cent = fantasy - mean(fantasy, na.rm = TRUE),
         perspective_cent = perspective - mean(perspective, na.rm = TRUE))%>% 
  select(sess_id, triad_id, distress_cent, empathic_cent,
         fantasy_cent, perspective_cent) %>% 
  right_join(integrated_profiles)
```

### Empathy Moderating Consensus
#### Distress moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distress_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distress_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distress_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distress_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_distress}
integrated_consensus_sam_distress <- lmer(p2 ~ p1_norm + p1_dist + eval + distress_cent +
                               distress_cent:p1_norm + distress_cent:p1_dist + 
                                 distress_cent:eval +
                               (1 + p1_norm + p1_dist + distress_cent +
                                  distress_cent:p1_norm + 
                                  distress_cent:p1_dist + distress_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_distress)
```

#### Empathic Concern moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}EmpathicConcern_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}EmpathicConcern_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}EmpathicConcern_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}EmpathicConcern_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_empathic}
integrated_consensus_sam_empathic <- lmer(p2 ~ p1_norm + p1_dist + eval + empathic_cent +
                               empathic_cent:p1_norm + 
                                 empathic_cent:p1_dist + empathic_cent:eval +
                               (1 + p1_norm + p1_dist + empathic_cent +
                                  empathic_cent:p1_norm + 
                                  empathic_cent:p1_dist + empathic_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_empathic)
```

#### Fantasy moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Fantasy_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Fantasy_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Fantasy_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Fantasy_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_fantasy}
integrated_consensus_sam_fantasy <- lmer(p2 ~ p1_norm + p1_dist + eval + fantasy_cent +
                               fantasy_cent:p1_norm + fantasy_cent:p1_dist + 
                                 fantasy_cent:eval +
                               (1 + p1_norm + p1_dist + fantasy_cent +
                                  fantasy_cent:p1_norm + fantasy_cent:p1_dist + 
                                  fantasy_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_fantasy)
```

### Perspective Taking moderating Hearsay consensus
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveP1_{it} + \pi_{2tg}NormativeP1_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

#### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}PerspectiveTaking_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}PerspectiveTaking_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}PerspectiveTaking_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}PerspectiveTaking_{tg} + r_{2tg}$    

#### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_consensus_x_perspective}
integrated_consensus_sam_perspective <- lmer(p2 ~ p1_norm + p1_dist + eval + perspective_cent +
                               perspective_cent:p1_norm + 
                                 perspective_cent:p1_dist + perspective_cent:eval +
                               (1 + p1_norm + p1_dist + perspective_cent +
                                  perspective_cent:p1_norm + 
                                  perspective_cent:p1_dist + perspective_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_consensus_sam_perspective)
```

### Empathy Moderating Accuracy
#### Distress moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Distress_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Distress_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Distress_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Distress_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_distress}
integrated_accuracy_sam_distress <- lmer(p2 ~ self_norm + self_dist + eval + distress_cent +
                               distress_cent:self_norm + distress_cent:self_dist +
                                 distress_cent:eval +
                               (1 + self_norm + self_dist + distress_cent +
                                  distress_cent:self_norm + 
                                  distress_cent:self_dist + distress_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_distress)
```

#### Empathic Concern moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}EmpathicConcern_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}EmpathicConcern_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}EmpathicConcern_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}EmpathicConcern_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_empathic}
integrated_accuracy_sam_empathic <- lmer(p2 ~ self_norm + self_dist + eval + empathic_cent +
                               empathic_cent:self_norm + empathic_cent:self_dist + 
                                 empathic_cent:eval +
                               (1 + self_norm + self_dist + empathic_cent +
                                  empathic_cent:self_norm + 
                                  empathic_cent:self_dist + empathic_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_empathic)
```

#### Fantasy moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}Fantasy_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}Fantasy_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}Fantasy_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}Fantasy_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_fantasy}
integrated_accuracy_sam_fantasy <- lmer(p2 ~ self_norm + self_dist + eval + fantasy_cent +
                               fantasy_cent:self_norm +
                                 fantasy_cent:self_dist + fantasy_cent:eval +
                               (1 + self_norm + self_dist + fantasy_cent +
                                  fantasy_cent:self_norm + 
                                  fantasy_cent:self_dist + fantasy_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_fantasy)
```

#### Perspective Taking moderating Hearsay accuracy
$P2_{itg} = \pi_{0tg} + \pi_{1tg}DistinctiveSelf_{it} + \pi_{2tg}NormativeSelf_{i} + \pi_{3tg}EvaluativenessProfile_{i} + \epsilon_{itg}$

##### Level 2 Equation: 
$\pi_{0tg} = \beta_{00g} + \beta_{01g}PerspectiveTaking_{tg} + r_{0tg}$   
$\pi_{1tg} = \beta_{10g} + \beta_{11g}PerspectiveTaking_{tg} + r_{1tg}$   
$\pi_{2tg} = \beta_{20g} + \beta_{21g}PerspectiveTaking_{tg} + r_{2tg}$   
$\pi_{3tg} = \beta_{30g} + \beta_{31g}PerspectiveTaking_{tg} + r_{2tg}$    

##### Level 3 Equation:
$\beta_{00g} = \gamma_{000} + u_{00g}$   
$\beta_{01g} = \gamma_{010} + u_{01g}$   
$\beta_{10g} = \gamma_{100} + u_{10g}$   
$\beta_{11g} = \gamma_{110} + u_{11g}$   
$\beta_{20g} = \gamma_{200} + u_{20g}$   
$\beta_{21g} = \gamma_{210} + u_{21g}$   
$\beta_{30g} = \gamma_{300} + u_{30g}$   
$\beta_{31g} = \gamma_{310} + u_{31g}$

```{r integrated_accuracy_x_perspective}
integrated_accuracy_sam_perspective <- lmer(p2 ~ self_norm + self_dist + eval + perspective_cent +
                               perspective_cent:self_norm + 
                                 perspective_cent:self_dist + perspective_cent:eval +
                               (1 + self_norm + self_dist + perspective_cent +
                                  perspective_cent:self_norm + 
                                  perspective_cent:self_dist + perspective_cent:eval | 
                                  sess_id/triad_id),
                             data = integrated_profiles)
summary(integrated_accuracy_sam_perspective)
```